Racets: Policy{-}Agnostic Programming in Racket

### 2018-07-23 paper/paper.tex
small tweaks

\begin{lstlisting}[language=Racket,escapechar=|,name=example]
  (define alice-board
          (facet alice-label (add-pieces (makeboard) x|$_1$| y|$_1$| |$...$|) star))
\end{lstlisting}

@@

\begin{figure}
\begin{displaymath}
  \begin{array}{lcrcl}
    \blue{c} & \blue{\in} & \blue{const} & \blue{::=} & \blue{() \mid \code{true} \mid \code{false} \mid \ldots} \\
    \blue{x} & \blue{\in} & \blue{var} & \blue{::=} & \blue{\ldots}  \\
    \blue{e} & \blue{\in} & \blue{exp} & \blue{::=} & \blue{c} \mid \blue{x} \\
    & & & \blue{\mid} & \blue{(\lambda ~ (x) ~ e) \mid (e ~ e)} \\
    & & & \blue{\mid} & \blue{(\code{box} ~ e) \mid (\code{unbox} ~ e) \mid (\code{set!} ~ e ~ e)} \\
    & & & \blue{\mid} & \blue{(\code{let-label} ~ \ell ~ e ~ e)} \\
    & & & \blue{\mid} & \blue{(\code{facet} ~ e ~ e ~ e)} \\
    & & & \blue{\mid} & \blue{(\code{obs} ~ e ~ e ~ e)} \\
  \end{array}
\end{displaymath}
\label{fig:syntax}
\caption{Syntax of \lang}
\end{figure}

>>>>

\begin{lstlisting}[language=Racket,escapechar=|,name=example]
  (define alice-board
          (facet alice-label (add-pieces (makeboard) x|$_1$| y|$_1$| |$...$|) (|\bmth{\star}|)))
\end{lstlisting}

@@

\begin{figure}
\begin{displaymath}
  \begin{array}{lcrcl}
    \blue{c} & \blue{\in} & \blue{const} & \blue{::=} & \blue{() \mid \code{true} \mid \code{false} \mid \ldots} \\
    \blue{x} & \blue{\in} & \blue{var} & \blue{::=} & \blue{\ldots}  \\
    \blue{e} & \blue{\in} & \blue{exp} & \blue{::=} & \blue{c} \mid \blue{x} \\
    & & & \blue{\mid} & \blue{(\lambda ~ (x) ~ e) \mid (e ~ e)} \\
    & & & \blue{\mid} & \blue{(\code{box} ~ e) \mid (\code{unbox} ~ e) \mid (\code{set!} ~ e ~ e)} \\
    & & & \fcol{\mid} & \fcol{(\code{let-label} ~ \ell ~ e ~ e)} \\
    & & & \fcol{\mid} & \fcol{(\code{facet} ~ e ~ e ~ e)} \\
    & & & \fcol{\mid} & \fcol{(\code{obs} ~ e ~ e ~ e)} \\
  \end{array}
\end{displaymath}
\label{fig:syntax}
\caption{Syntax of \lang. Forms unique to facets are shown in \fcol{red}.}
\end{figure}
